Data Preparation

### 2019-01-10 Data Preparation.Rmd
##Student data in Data Import description

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.

The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

>>>>

### Course Manuals
To expand our topic modeling of course content, we analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).

```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `d_transcripts` contains the transcripts information of students as was provided. It has 40 columns, and rows correspond to a type of grade (e.g. final grade, attendance) per student per course per time they took it.
